\chapter{Glossary}

This document defines key terms for the Into the Grid project.

\section{Player}

The player in Into the Grid can be an Universe Designer (see below) or join into an existing Universe game. Players joining into a game may choose their Empire and its ship types.

\section{Player Objective}


A player's objective depends on their Empire but mainly consist of these types:

\begin{itemize}
	\item Discovery - discover a number of planet types
	\item Aggression - find and conquer other ships
	\item Universe Designer
\end{itemize}

This is the player responsible for designing the universe for one particular game. The player may choose different Universe Templates that decide which Empire joining characters can play.

\section{Universe}

Into the Grid's two dimensional visual representation of a section of a space universe.
It is divided into 8 by 8 grid sectors and contains the following game items:

\begin{itemize}
	\item Players' ships
	\item Planets
	\item Stars
	\item Bases
	\item Universe Resources
\end{itemize}

Each universe contains a number of planets, stars, and bases. These are randomly distributed around the Universe's grids. Bases can be used to replenish ship supplies or be allied to an opposing Empire meaning they might attack player Ships. Stars and planets enhance the appearance of the universe.

\section{Universe Template}

 A player may configure the game's Universe by applying a custom or preexisting template which can change the following game items and mechanics:

\begin{itemize}
	\item Universe Lore ("Star Wars" or a player's custom scenario lore)
	\item Ship Types
	\item Weapons
	\item Ships
\end{itemize}

Players can choose a variety of spaceships within their chosen Empire. These spaceships can come in a variety of types such as Bird of Prey and a Federation Starship. Each type has unique capabilities such as:

\begin{itemize}
	\item Max Speed
	\item Warp Speed/Max Warp Speed
	\item Amount of energy available
	\item Weapons
	\item Number of crew
	\item Shield Capacity
	\item The ability to cloak
	\item Shield Levels - color coded red, yellow, and green representing shield integrity levels.
	\item Ship Weapon Types
\end{itemize}

 Each ship has two types of attacks: Energy and Missiles. Depending on the ship's Empire, ships may be equipped with Phasers (using energy) or Photon Torpedoes (expending missiles)  which deal different amounts of damage to other ships. Each Empire Ship Type has different types of weapons that have a damage amount and range to it.

\section{Empire}

An empire is an in-game faction group consisting of the following attributes:
\begin{itemize}
	\item Type (identifying as Federation, Klingon, etc.)
	\item Ships
	\item Alliances
	\item Stardate
\end{itemize}

 A stardate is a unit of in-game time that spans an arbitrary amount of real world time. Stardate dictates the following mechanics of the game:
 Every game turn increments the stardate by one
 Game missions have a stardate requirement (e.g. explore the sector by some star date

\section{Custom Scenarios/Universe Builder}

Into the grid allows players to customize their player experience by giving the tools needed to modify game Empires and ships to their own specifications.

\section{Player Turn}

A player turn consists of several actions available to him/her such as:

\begin{itemize}
	\item Navigating a ship
	\item Attacking other ships
	\item Setting ship shield levels
	\item Cloak
	\item Self Destruct
	\item Transfer crew into another ship to capture it
	\item Jettison Ship during a self destruct sequence)
\end{itemize}
