\chapter{Supplementary Specification}

\section{Introduction}

This document contains all requirements not contained in the use cases.

\section{Functionality}

\subsection{System Features}

The Game system shall provide these features:

\begin{itemize}
	\item Players may create a universe that other players can join.
	\item Diverse game objectives that can be chosen by a player.
	\item A ''modifiable'' aspect where users can create their own assets and scenarios.
	\item  multiplayer and single player turn-by-turn strategy game mechanic.
	\item Game opponents who have their own AI.
	\item The ability to save and load games.
	\item Generating reports: overview and detailed report of game statistics.
	\item Logging and Error Handling
\end{itemize}

Should an unexpected error occur:

\begin{itemize}
	\item Client log diagnostic/error information to a file
	\item Display user friendly error message
	\item Server has a snapshot ability to restore a game on client/server crash
\end{itemize}

\subsection{Usability}

The game interface is designed such that a player who is familiar with turn based strategy games can learn how to play the game by reading the game user guide in at most five minutes.

\subsection{Reliability}

The game system shall perform without crashes during usage.

\subsection{Performance}

\begin{itemize}
	\item One game server shall support up to 500 player clients simultaneous.
	\item One game server shall support multiple "Universes"
	\item One game client shall be able to join an unlimited number of game servers.
	\item Every client action shall be acknowledged by server within one second.
\end{itemize}

\subsection{Supportability}

\begin{itemize}
	\item The game client shall allow key configuration parameters (asset folders, connection settings) to be specified in a configuration file.
	\item Implementation Restraints
	\item The game server shall use Java 7 as the back-end.
	\item The game client shall use Java 7 Swing as the GUI front-end to interconnect with the back-end.
	\item The game client/server will support any Operating System that is compatible with Java.
\end{itemize}

\subsection{Reports}

The game shall provide the following reports:

\begin{itemize}
	\item Universe Status Summary
	\begin{itemize}
		\item For a given "Universe", this displays the statistics of in-game Players (Ships commanded, Faction) and summary of the contents of each sector with Current Star Date.
	\end{itemize}
	\item Sector Detail
	\begin{itemize}
		\item Shows a list of all entities and ship statuses within.
	\end{itemize}
\end{itemize}
