\chapter{Use Cases}

\section{Connect To Server}
\subsection{Actors}
\begin{itemize}
	\item Player
\end{itemize}

\subsection{Preconditions}
\begin{itemize}
	\item Player has started up the game and is viewing the "Connect to Server" screen.
\end{itemize}

\subsection{Postconditions}
\begin{itemize}
	\item The player gains access to the server's games.
\end{itemize}

\subsection{Main Success Scenario}
\begin{enumerate}
	\item Player enters valid information.
	\item System validates the information entered by the user and gives the user access to server's games.
\end{enumerate}

\subsection{Extensions}
2a. System detects a missing or invalid username.
\begin{enumerate}
	\item System displays an error and informs the player.
	\item Player enters their username.
\end{enumerate}

2b. System detects a missing or invalid password.
\begin{enumerate}
	\item System displays an error and informs the player.
	\item Player enters their password.
\end{enumerate}

2c. System detects a missing or invalid server address.
\begin{enumerate}
	\item System displays an error and informs the player.
	\item Player enters a server address.
\end{enumerate}

2d. System detects a missing or invalid port number.
\begin{enumerate}
	\item System displays an error and informs the player.
	\item Player enters a port number.
\end{enumerate}

\section{Restore Game}

\subsection{Preconditions}
\begin{itemize}
	\item The player has logged in to the system.
\end{itemize}

\subsection{Postconditions}
\begin{itemize}
	\item The game is restored.
\end{itemize}

\subsection{Main Success Scenario}
\begin{enumerate}
	\item The player requests to restore a game.
	\item The system prompts the player for the file the saved game resides in.
	\item The player selects the file the saved game resides in.
	\item The system restores the game and adds it to the list of games.
\end{enumerate}

\subsection{Extensions}
3a. The system detects that the file is not valid.
\begin{enumerate}
	\item The system notifies the user that the file is not valid.
\end{enumerate}

\section{Join Game}

\subsection{Actors}
\begin{itemize}
	\item{Player}
\end{itemize}

\subsection{Preconditions}
\begin{itemize}
	\item Player has connected to the server and is viewing the list of available games to join.
\end{itemize}

\subsection{Postconditions}
\begin{itemize}
	\item Player joins an available game.
\end{itemize}

\subsection{Main Success Scenario}
\begin{enumerate}
	\item The player selects a game from the list of current games.
	\item The system prompts the player for an empire and ship type.
	\item The player provides their desired empire and ship type.
	\item The system joins the player to the game.
\end{enumerate}

\subsection{Extensions}
1a. System detects that the user is returning to the game.
\begin{enumerate}
	\item The player resumes their game.
\end{enumerate}

\section{Execute Command}

\subsection{Actor}
\begin{itemize}
	\item Player
\end{itemize}

\subsection{Preconditions}
\begin{itemize}
	\item The player's command is executed.
\end{itemize}

\subsection{Main Success Scenario}
\begin{enumerate}
	\item The player chooses a command to execute.
	\item The system processes the command entered by the player and relays the result of the command.
\end{enumerate}

\subsection{Extensions}
1a. The player selects the ''Navigate'' action.
\begin{enumerate}
	\item The system prompts the player for a destination.
	\item The player selects a desired destination.
		\begin{enumerate}
			\item No energy remains:
				\begin{enumerate}
					\item The action is not executed.
				\end{enumerate}
		\end{enumerate}
\end{enumerate}

1b. The player selects the ''Set Alert'' action.
\begin{enumerate}
	\item The system prompts the user for the desired alert level.
	\item The player selects the desired alert level.
\end{enumerate}

1c. The player selects the ''Fire Torpedo'' action.
\begin{enumerate}
	\item The system prompts the player for a target.
	\item The player selects a desired target.
\end{enumerate}

1 - 2a. The player selects the ''Refresh'' action.
\begin{enumerate}
	\item The system gets the latest information from the server.
\end{enumerate}
