\chapter{User Guide}

\section{Running the Application}

\subsection{Server}
Download the deployment.zip.
Unzip the contents of the deployment zip and run the server.sh script \textbf{OR}  run the command listed in the README to run on a non-default port.

\subsection{Other Instructions}
To stop the server, type '/exit' in the command box and press enter.

\subsection{Client}

\subsubsection{Joining a Game}
Download the deployment.zip.
Unzip the contents of the deployment.zip and run the client.sh script.
Run the client.sh script, a 'Connect to Server' dialog box will appear.
Enter server address and port details (port 8080 by default).
Enter username and password (in this stage, all passwords must 'p'.
A 'Server Game List' dialog box will appear.
Clock 'Restore Game' to open the file chooser.
Locate and select a valid save file; this will restore the game to the server.
Now the game should appear in the games list window.
Select the game from the list and click 'Join'.
If this is your first time joining, you will be prompted to select your empire and ship type.
After this, the main game window will appear.

\subsubsection{Performing Actions}
\begin{description}
    \item [Warp]
    Click 'Warp' and then click the desired sector.
    \item [Navigate]
    Click 'Impulse' and then click the desired location within the sector.
    \item [Fire Torpedo]
    Click 'Missile' and then click the desired target.
    \item [Alert Level]
    Click the desired alert level radio button
    \item [Refresh]
    Click 'Refresh'.
\end{description}
